### 2011-03-07 standing-patches-paper.tex
/* Hitchhiking */

@@

>>>>

Reference on parallel adapation, standing variation, etc.:
 coop,
 pennings and hermisson,

@@

For now we ignore geographic hetergeneity, and assume that the species range
is a homogenous, two-dimensional region.  (results for a one-dimensional region also appear)
There are two selective types -- the neutral type, and the mutated type.
We assume that different mutations are distinguishable --
either as selectively equivalent mutations, or by linked variation.
At first, the mutated type is at a seletive disadvantage, for long enough to be at selection-mutation equilibrium,
but at a certain time the selective regime changes, so that the mutated type has a selective advantage and quickly spreads to fixation.
After fixation, alleles are either descended
from families of mutants present as standing variation when the selective regime changed,
or from new mutants arising since that time.

We will suppose that before time $t=0$,
the mutant type has fitness $1-s_d$ relative to the neutral type,
and that after time $t=0$,
the mutant type has fitness $1+s_b$,
for positive numbers $s_d$ and $s_b$.
We assume that diploid fitness is additive, or at lesat that the important dynamics are determined by the haploid fitness.
If the mutation is recessive, XXX more complicated things happen.
More concretely, suppose that the species occupies an area with mean density
